% Curriculum vitae

% Lincoln A. Mullen | lincoln@lincolnmullen.com | https://lincolnmullen.com

\documentclass[11pt]{article}
\usepackage{microtype}
\frenchspacing
\usepackage[letterpaper,margin=1in]{geometry} 
\setlength\parindent{0in}
\setlength\parskip{6pt}
\setlength{\emergencystretch}{3em}
% \def\ind{\hangindent=1 true cm\hangafter=1 \noindent}
\usepackage[osf,sc]{mathpazo}
\usepackage{inconsolata}
\usepackage{fancyhdr}
\pagestyle{plain}
\frenchspacing
% \usepackage{multicol}
% \usepackage{graphicx}
% \usepackage[usenames,dvipsnames]{color}

% % ---- MARGIN YEARS
% \usepackage{marginnote}
% \newcommand{\years}[1]{\marginnote{#1}[4pt]}
% \renewcommand{\raggedleftmarginnote}{}
% \setlength{\marginparsep}{2pt}
% \reversemarginpar

% HEADINGS
\usepackage{sectsty} 
\usepackage{titlesec}
\usepackage[normalem]{ulem} 
\sectionfont{\rmfamily\mdseries\Large} 
\subsectionfont{\rmfamily\mdseries\scshape\normalsize} 
\subsubsectionfont{\rmfamily\bfseries\upshape\normalsize} 
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsubsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
% disables chapter, section and subsection numbering
\setcounter{secnumdepth}{-1} 

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% PDF SETUP
\PassOptionsToPackage{hyphens}{url}\usepackage[hidelinks, breaklinks, pdftex, pdftitle={Lincoln A.  Mullen - CV}, pdfauthor={Lincoln A. Mullen}]{hyperref}  

% DOCUMENT
\begin{document}
\thispagestyle{fancy}
\fancyfoot{}
\fancyhead{}
\renewcommand{\headrulewidth}{0pt}
%%% The next line will put the date revised in footer of first page
\rfoot{\scriptsize Current as of \today}

\hfill\hfill\hfill
\hfill\hfill\hfill
\hfill\hfill\hfill
\hfill\hfill\hfill
\begin{minipage}[t]{1.6in}
  \flushleft{\scriptsize  \texttt{\href{mailto:lincoln@lincolnmullen.com}{lincoln@lincolnmullen.com}}} \\
  \vspace{-0.065in}{\scriptsize  \url{https://lincolnmullen.com}} \\
  \vspace{-0.065in}{\scriptsize  ORCID: 
  \href{https://orcid.org/0000-0001-5103-6917}{\texttt{0000-0001-5103-6917}}}
\end{minipage}
\hfill
\begin{minipage}[t]{1.9in}
  \flushleft{{\scriptsize {Department of History \& Art History} \\ George 
      Mason University \\ 4400 University Drive, MSN 3G1 \\ \vspace{-0.05in} 
      Fairfax, VA 22030}}
\end{minipage}

\vspace{0.1in}

{\Large Lincoln A. Mullen}\\[-0.1in]

\subsection{appointments}\label{Appointments}


Associate professor, Dept. of History \& Art History, George Mason University (2019--).

Director of computational history, Roy Rosenzweig Center for History and New Media (2018--).

Assistant professor, Dept. of History \& Art History, George Mason University (2014--2019).

\subsection{education}\label{education}

PhD history, Brandeis University (2014). 

MA history, Brandeis University (2011).

BA \& MA history, Bob Jones University (2006/2008).

\subsection{books}\label{books}

\emph{America's Public Bible: Biblical Quotations in U.S. Newspapers} (Stanford University Press, under contract). \url{https://americaspublicbible.org}.

\emph{The Chance of Salvation: A History of Conversion in America} (Harvard University Press, 2017). \url{https://www.hup.harvard.edu/catalog.php?isbn=9780674975620}.

\subsection{collaborative digital projects}\label{digital projects}

\emph{American Religious Ecologies}, Roy Rosenzweig Center for History and New Media, George Mason University (in progress, 2018--): \url{https://religiousecologies.org}. (project director)

\emph{Collecting These Times: American Jewish Experiences of the Pandemic}, Roy Rosenzweig Center for History and New Media, George Mason University (in progress, 2021--): \url{https://collectingthesetimes.org}. (co-project director)

\emph{Pandemic Religion: A Digital Archive}, Roy Rosenzweig Center for History and New Media, George Mason University (in progress, 2020--): \url{https://pandemicreligion.org}. (co-project director)

\emph{Mapping Early American Elections}, Roy Rosenzweig Center for History and New Media, George Mason University (2016--2019): \url{https://earlyamericanelections.org}. (project director)

\subsection{peer-reviewed journal articles \& book chapters}\label{peer-reviewed}

Stephen Robertson and Lincoln A. Mullen, ``Arguing with Digital History: 
Patterns of Historical Interpretation,'' \emph{Journal of Social History} 54, 
no. 4 (2021): 1005--1022, \url{https://doi.org/10.1093/jsh/shab015}.

Stephen Robertson and Lincoln A. Mullen, ``Navigating through Narrative,'' in 
\emph{Making Deep Maps: Foundations, Approaches, and Methods}, edited by David 
Bodenhamer, John Corrigan, and Trevor Harris (Routledge, 2021), 132--147, 
\url{https://doi.org/10.4324/9780367743840-8}.

``The Making of America's Public Bible: Computational Text Analysis in Religious History,'' in \emph{Introduction to Digital Humanities: Research Methods for the Study of Religion}, edited by Christopher D. Cantwell and 
Kristian Petersen (DeGruyter, 2021), 31--52, \url{https://doi.org/10.1515/9783110573022-003}.

``A Braided Narrative for Digital History,'' in \emph{Debates in the Digital Humanities 2019}, ed. Matthew K. Gold and Lauren F. Klein (University of Minnesota Press, 2019), 382--388, \url{ https://doi.org/10.5749/j.ctvg251hk.34}.

Ben Marwick, Carl Boettiger, and Lincoln A. Mullen, ``Packaging Data Analytical Work Reproducibly using R (and Friends)'' \emph{American Statistician} 72, no. 1 (2018): 80--88, \url{https://doi.org/10.1080/00031305.2017.1375986}.

Kellen Funk and Lincoln A. Mullen, ``The Spine of American Law: Digital Text Analysis and U.S. Legal Practice,'' \emph{American Historical Review} 123, no.  1 (2018): 132--164, \url{https://doi.org/10.1093/ahr/123.1.132}.

``Bibles and Tracts in Print Culture in America,'' \emph{Oxford Research Encyclopedia of Religion} (Oxford University Press, 2017). \url{ https://doi.org/10.1093/acrefore/9780199340378.013.412}.

Cameron Blevins and Lincoln A. Mullen, ``Jane, John \ldots{} Leslie? A Historical Method for Algorithmic Gender Prediction,'' \emph{Digital Humanities Quarterly} 9, no. 3 (2015): \url{http://www.digitalhumanities.org/dhq/vol/9/3/000223/000223.html}. 

``The Contours of Conversion to Catholicism in the Nineteenth Century,'' \emph{U.S. Catholic Historian} 32, no. 2 (2014): 1--27, \url{https://doi.org/10.1353/cht.2014.0007}. 

``Using Metadata and Maps to Teach the History of Religion,'' \emph{Transformations: The Journal of Inclusive Scholarship and Pedagogy}, 25, no. 1 (2014): 112--118, \url{https://doi.org/10.1353/tnf.2014.0008}.

% ``Confessionalization and the Creedal Tradition,'' \emph{The Proceedings of the South Carolina Historical Association} (March 2010): 79--90.

\subsection{other academic publications}\label{other-academic}

``Christian Missions to the Jews: Joseph Krauskopf on 'Jewish Converts, Perverts, and Dissenters,'\,'' in \emph{Key Texts in American Jewish History: A Tribute to Jonathan D. Sarna}, edited by Mark A. Raider and Gary P. Zola (Brandeis University Press, forthcoming).

Lincoln A. Mullen, Margaret Bendroth, Thomas Kidd, Keith Harper, and Robert W. 
Prichard, ``The Uses of Denominational History,'' \emph{Fides et Historia} 49, 
no. 2 (2017): 57--66.

Arguing with Digital History working group, ``Digital History and Argument,'' 
white paper, Roy Rosenzweig Center for History and New Media (November 13, 
2017): \url{https://rrchnm.org/argument-white-paper/}.

Kellen Funk and Lincoln A. Mullen, ``A Servile Copy: Text Reuse and Medium Data 
in American Civil Procedure,'' in \emph{Forum: Die geisteswissenschaftliche 
  Perspektive: Welche Forschungsergebnisse lassen Digital Humanities 
  erwarten?} [\emph{Forum: With the Eyes of a Humanities Scholar: What Results 
  Can We Expect from Digital Humanities?}], 24 \emph{Rechtsgeschichte} 
[\emph{Legal History}] (2016): 341--43, 
\url{https://doi.org/10.12946/rg24/341-343}.

``Lynching, Visualization, and Visibility,'' \emph{Journal of Southern 
  Religion} 17 (2015): \url{http://jsreligion.org/issues/vol17/mullen.html}.

``Digital Humanities Is a Spectrum; or, We're All Digital Humanists
Now,'' in Melissa Terras, Edward Vanhoutte, and Julianne Nyhan, eds.,
\emph{Defining Digital Humanities: A Reader} (Ashgate, 2013), 237--38.

``A Narrative of the Troubles in the Second Church in Windsor,
1735--1741,'' by Roger Wolcott, \emph{Journal of Jonathan Edwards
  Studies} 2, no. 2 (2012): 83--142.

\subsection{peer-reviewed academic software}\label{academic-software}

Lincoln A. Mullen et al., ``Fast, Consistent Tokenization of Natural Language 
Text,'' \emph{Journal of Open Source Software} 3, no. 23: 655 (2018), 
\url{https://doi.org/10.21105/joss.00655}.

Lincoln A. Mullen and Jordan F. Bratt, ``USAboundaries: Historical and 
Contemporary Boundaries of the United States of America,'' \emph{Journal of 
Open Source Software} 3, no. 23 (2018): 314, 
\url{https://doi.org/10.21105/joss.00314}.

``textreuse: Detect Text Reuse and Document Similarity,'' R package published 
by rOpenSci (2015--): 
\url{https://github.com/ropensci/textreuse}.

\subsection{selected other academic software and visualizations}\label{other-academic-software}

``gender: Predict Gender from Names Using Historical Data,'' R package 
published by rOpenSci (2014--): \url{https://github.com/ropensci/gender}.

``internetarchive: An R client to the Internet Archive API,'' R package 
published by rOpenSci (2015--): 
\url{https://github.com/ropensci/internetarchive}.

``historydata: Datasets for Historians'' R package published by rOpenSci 
(2014--):  
\url{https://github.com/ropensci/historydata}.

% ``Divergence in U.S. Sex Ratios by County, 1820--2010:'' 
% \url{http://lincolnmullen.com/projects/sex-ratios/}.

``The Spread of U.S.  Slavery, 1790--1860'':  
\url{http://lincolnmullen.com/projects/slavery/}.

``Historical Boundaries of the United States, 1783--1912'': 
\url{http://lincolnmullen.com/projects/us-boundaries/}.

% ``Paulists Missions, 1851--1906'': 
% \url{http://lincolnmullen.com/projects/paulists-map/}.

% Erin M. Bartram and Lincoln A. Mullen, \emph{The American Converts Database} 
% (2013--15). \url{http://americanconverts.org}

\subsection{reviews}\label{book-reviews}

Review of \emph{Jews on the Frontier: Religion and Mobility in Nineteenth-Century America}, by Shari Rabin, \emph{American Religion} 2, no. 2 (2021): 166--168, \url{https://doi.org/10.2979/amerreli.2.2.18}.

Review of \emph{The Oxford Handbook of the Bible in America}, edited by Paul 
C. Gutjahr, \emph{Journal of American History} 105, no. 4 (2019): 987--989, \url{https://doi.org/10.1093/jahist/jaz026}.

Review of \emph{Christian: The Politics of a Word in America}, by Matthew 
Bowman, \emph{Reading Religion}, August 2018: 
\url{http://www.readingreligion.org/books/christian}.

Review of \emph{Evangelical Gotham: Religion and the Making of New York City, 
  1783--1860}, by Kyle B. Roberts, \emph{Religion in American History}, March 
28, 2017: 
\url{http://usreligion.blogspot.com/2017/03/the-places-of-evangelical-gotham.html}.

Review of \emph{The Programming Historian}, 2nd ed., edited by
Adam Crymble, et al., \emph{Journal of American History} 103, no. 1 (2016): 
299--301, \url{https://doi.org/10.1093/jahist/jaw172}.

Review of \emph{Guaranteed Pure: The Moody Bible Institute, Business, and the 
  Making of Modern Evangelicalism}, by Timothy E. W. Gloege, \emph{Religion in 
  American History}, July 1, 2015: 
  \url{http://usreligion.blogspot.com/2015/07/the-business-practices-of-corporate.html}.

Review of \emph{One Nation Under God: How Corporate America Invented Christian 
  America}, by Kevin M. Kruse, \emph{Religion in American History}, April 1, 
2015: 
\url{http://usreligion.blogspot.com/2015/04/christian-nation-christian.html}.

% Review of \emph{Religion and the Marketplace in the United States},
% edited by Jan Stievermann, Philip Goff, Detlef Junker, Anthony Santoro,
% and Daniel Silliman, \emph{Religion in American History}, February 1,
% 2015.

Review of \emph{The Age of Atheists: How We Have Sought to Live Since
  the Death of God}, by Peter Watson, \emph{Books and Culture}, August
2014: 
\url{https://www.booksandculture.com/articles/webexclusives/2014/august/age-of-atheists.html}.

Review of \emph{By the Rivers of Water: A Nineteenth-Century Atlantic
  Odyssey}, by Erskine Clarke, \emph{Religion in American History},
December 1, 2013: 
\url{http://usreligion.blogspot.com/2013/12/from-rivers-of-water-to-river-of-dark.html}.

Review of \emph{Teaching History in the Digital Age}, by T. Mills Kelly,
\emph{ProfHacker}, \emph{Chronicle of Higher Education}, August 26,
2013: 
\url{https://www.chronicle.com/blogs/profhacker/learning-how-to-teach-history-in-a-digital-age/51875}.

Review of \emph{Chosen People: The Rise of American Black Israelite
  Religions}, by Jacob S. Dorman, \emph{Religion in American History}, May
1, 2013: 
\url{http://usreligion.blogspot.com/2013/05/jacob-dorman-on-rise-of-black-israelite.html}.

Review of \emph{The Science of the Soul in Colonial New England}, by
Sarah Rivett, \emph{Religion in American History}, December 17, 2012: 
\url{http://usreligion.blogspot.com/2012/12/the-science-of-soul-in-colonial-new.html}.

Review of \emph{A Theology of Religious Change: What the Social Science
  of Conversion Means for the Gospel}, by David J. Zehnder, \emph{Journal
  of Markets and Morality} 15, no. 1 (2012): 249--250.

Review of \emph{Evangelism and Resistance in the Black Atlantic,
  1760--1835}, by Cedrick May, \emph{Journal of Southern Religion}, 13
(2011).

Review of \emph{The Gardiners of Massachusetts: Provincial Ambition and
  the British-American}, by T. A. Milford, \emph{Historical Journal of
  Massachusetts} 39, nos. 1--2 (2011): 265--66.

Review of \emph{Daily Lives of Civilians in Wartime Early America: From
  the Colonial Era to the Civil War}, edited by David S. Heidler and
Jeanne T. Heidler, \emph{Army History} 78 (2011): 44--45.

Review of \emph{In the Beginning: Fundamentalism, the Scopes Trial, and
  the Making of the Antievolution Movement}, by Michael Lienesch,
\emph{The Southern Historian} 30 (2009): 103--5.

\subsection{selected media publications \& interviews}\label{public}

``Library of Congress Looks to AI to Help Users Sift Through Its Collection,''
\emph{Wall Street Journal}, June 24, 2021:
\url{https://www.wsj.com/articles/library-of-congress-looks-to-ai-to-help-users-sift-through-its-collection-11624552197}.

Zev Eleff, Shulamith Z. Berger, Joshua Furman, Jeremy R. Katz, Lincoln Mullen,
Josh Parshall, Rebekah Sobel, and John Turner, ``Preserving These Moments: A
Call to Action for the American Jewish Community,'' \emph{e-Jewish
Philanthropy}, July 24, 2020: \url{https://ejewishphilanthropy.com/preserving-these-moments-a-call-to-action-for-the-american-jewish-community/}.

``Conversion in America: A Conversation with Lincoln Mullen,'' Interview with
Kristian Petersen for the American Academy of Religion podcast, April 18, 2019: \url{https://www.aarweb.org/AARMBR/Resources-/Webinars-and-Podcasts-/Conversion-in-America.aspx}.

``The Fight to Define Romans 13,'' \emph{The Atlantic}, June 15, 2018: \url{https://www.theatlantic.com/politics/archive/2018/06/romans-13/562916/}.

``Convert Nation,'' interview by Emma Green, \emph{The Atlantic}, August 12, 
2017: \url{https://www.theatlantic.com/politics/archive/2017/08/conversions-lincoln-mullen/536151/}

``NEH Data Challenge Winner: America's Public Bible,'' National Endowment for 
the Humanities, April 24, 2017: 
\url{https://www.neh.gov/divisions/preservation/featured-project/neh-data-challenge-winner-americas-public-bible}.

``Newspapers were once full of Bible quotes---and a local professor's tool lets 
us learn from them,'' by Julie Zauzmer, \emph{Washington Post}, August 3, 2016: 
\url{https://wapo.st/2aLT1Zo}.

``Looking Back at Born Again,'' interview by Maureen Fiedler on \emph{Interfaith Voices}, public 
radio, July 8, 2016:  
\url{http://interfaithradio.org/Story_Details/Looking_Back_at___Born_Again__}.

``Just Another Sinner, Born Again,'' \emph{The Atlantic}, June 29, 2016: 
\url{http://www.theatlantic.com/politics/archive/2016/06/trump-born-again/489269/}.

``How to learn more about slavery after watching the new 'Roots'\,'' by Anthea Butler, \emph{Washington Post}, June 3, 2016: \url{http://wapo.st/1ZjJMif}.

``The spread of US slavery, in one haunting map,'' by German Lopez, 
\emph{Vox}, March 26, 2016: 
\url{https://www.vox.com/2016/3/26/11306912/slavery-map}.

``Catholics Who Aren't Catholic,'' \emph{The Atlantic}, September 8, 
2015:  
\url{http://www.theatlantic.com/politics/archive/2015/09/catholics-who-arent-catholic/404113/}.

``These Maps Reveal How Slavery Expanded Across the United States,''
\emph{Smithsonian.com}, May 15, 2014:
\url{http://www.smithsonianmag.com/history/maps-reveal-slavery-expanded-across-united-states-180951452/}.

% Former contributor to the \emph{Religion in American History} blog (2012--2016).

% Former contributor to \emph{ProfHacker}, a \emph{Chronicle of Higher Education} blog (2010--2014). 

\subsection{invited talks}\label{invited-talks}

``Using DataScribe for Large Scale Transcription Projects in the Humanities,'' invited talk at Digital Lagniappe, University of Southern Mississippi, April 16, 2021.

``From Infrastructure to Interpretation in the Digital History of American Religion,'' invited talk at the Centre for Contemporary and Digital History, University of Luxembourg, June 24, 2020. \url{https://www.youtube.com/channel/UCYAiQlEvXfu0diRaUC8lQFg}

Invited panelist for the symposium "Religion in Place: Spaces, Borders, Bodies," St. Louis University, St. Louis, MO, October 10--12, 2019.

``Towards Quantitative Cultural Histories in America's Public Bible,'' invited talk at the Center for Digital Humanities, Vanderbilt University, April 11, 2019.

Invited talk for "Workshop on Quantitative Analysis and the Digital Turn in Historical Studies," Fields Institute for Mathematical Studies, Toronto, Canada, February 27, 2019.

``Digital Sources and Methods in the Service of Historical Interpretations,'' 
invited talk for the National Endowment for the Humanities, November 28, 
2018.

``Finding Biblical Quotations in Historical Newspaper Corpora,'' invited talk for Math and Computer Science Colloquium, University of Richmond, October 29, 2018.

``The Chance of Salvation: How Americans Chose Their Religion,'' talk for Fall for the Book, October 11, 2018.

``Digital Literacies for History Undergraduates,'' invited talk at Brandeis University, September 28, 2018.

``The Bible in American History,'' invited panelist at the John W. Kluge Center, Library of Congress, June 7, 2018.

``Surveying the `Lost Atlantis' of Early American Politics,'' invited talk at 
Southern Methodist University, Dallas, TX, October 24, 2017.

``The Bible in the Newspaper: Computational Text Analysis for American 
Religious History,'' invited talk at St. Olaf's College, Northfield, MN, May 
9, 2017.

Kellen Funk and Lincoln A. Mullen, ``Text Reuse for Digital Legal History,'' 
invited talk and workshop, American Society for Legal History, Toronto, October 27, 2016.

``The Bible in the Newspaper,'' invited talk at the NEH National Digital Newspaper Program annual meeting, Washington, DC, September 14, 2016.

``Choosing the New Birth: The Protestant Development of the Sinner's Prayer in 
Early America,'' invited paper at the Virginia Colloquium in American 
Religion, University of Virginia, April 1, 2016.

\subsection{conference papers and workshops}\label{conference-papers}

``The Scholarly Primitives of Datafication in History,'' Datafication in the
Historical Humanities: Reconsidering Traditional Understandings of Sources and
Data, German Historical Institute, December 9--11, 2021.

John G. Turner and Lincoln A. Mullen, ``From \emph{Pandemic Religion} to \emph{Collecting These Times},'' Association of Jewish Libraries, June 28, 2021.

Chair and commentator for ``Eighteenth- and Nineteenth-Century Anti-Catholicism in America and its Legacies,'' American Society of Church History, Chicago, IL, January 6, 2019.

Panelist for ``Timothy Larsen's John Stuart Mill: A Secular Life and OUP's Spiritual Lives Series,'' American Society of Church History, Chicago, IL, January 3, 2019.

Invited participant at rOpenSci Unconference, Seattle, WA, May 21--22, 2018.

Invited participant at rOpenSci Text Developers Workshop, New York University, 
New York, April 20--21, 2017.

``Arguing with Digital History: A Roundtable on Using Digital History to Make 
Arguments for Academic Audiences,'' panel co-chair with Stephen Robertson, 
annual meeting of the American Historical Association, Washington, DC, January 
6, 2018.

``How 19th-Century Americans Quoted Their Bibles,'' paper presented at the 
annual meeting of the American Society of Church History, Washington, DC, 
January 4, 2018.

Arguing with Digital History workshop, organizer with Stephen Robertson, 
George Mason University, September 15--16, 2017.

Invited participant at rOpenSci Text Developers Workshop, London School of Economics, London, April 21--22, 2017.

``The Uses of Denominational History,'' panel chair and organizer for the annual meeting of the Conference on Faith and History, Virginia Beach, VA, October 21, 2016.

``Mapping Denominational Statistics in the Nineteenth Century,'' discussant 
for ``Digital Humanities Roundtable: Mapping the Early Republic,'' annual 
meeting of the Society for Historians of the Early American Republic, New 
Haven, July 21--24, 2016.

Guest faculty at Doing Digital History, NEH-ODH Summer Institute, George 
Mason University, Arlington, VA, July 14--18, 2016.

Lincoln A. Mullen and Kellen Funk, ``Detecting Text Reuse in Nineteenth-Century 
Legal Codes of Civil Procedure,'' presentation at the Digital Humanities 
Summer Institute Colloquium, University of Victoria, June 16, 2016.

Jason Heppler and Lincoln A. Mullen, ``R, Interactive Graphics, and Data 
Visualization for the Humanities,'' workshop for the Digital Humanities Summer 
Institute, University of Victoria, Canada, June 13--17, 2016.  

``The Religion of Children and Families in the Nineteenth-Century United 
States,'' paper presented at the annual meeting of the American Society of 
Church History, Atlanta, January 10, 2016.

Presentations on ``The Migration of the Field Code'' and ``Teaching 
Graduate Methods Courses with RStudio,'' Digital Research and Pedagogy 
Lightening Rounds, American Historical Association, January 2016.

``Data Visualization for Humanists,'' workshop at the University of Helsinki, 
Finland, December 16--18, 2015. 

Guest faculty at Getty Summer Institute on 
Digital Art History, George Mason University, Fairfax, VA, July 21, 2015.

Spatial humanities workshop, Concordia College, Moorhead, MN, June 1--5, 2015.  
\url{https://lincolnmullen.com/projects/spatial-workshop/}

``Converts and the Category of Irreligion in the Nineteenth-Century
United States,'' paper presented at the annual meeting of the
Organization of American Historians, St.~Louis, April 16--19, 2015.

Invited participant at rOpenSci Unconference, San Francisco, CA, March 26--27, 2015.

``Mapping Boston's Religions: Next Steps in Mapping U.S. Religious History,'' 
for the panel ``Mapping Religious Space: Four American Cities from the 
Colonial Era to the Twentieth Century'' at the annual meeting of the American 
Society of Church History, New York, January 2--5, 2015.  
\url{https://lincolnmullen.com/projects/asch-2015/}

``Teaching Graduate Students to Code,'' poster for the annual meeting of the
American Historical Association, New York, January 2--5, 2015.
\url{https://lincolnmullen.com/blog/poster-teaching-graduate-students-to-code/}

Guest faculty at Doing Digital History, NEH-ODH 
Summer Institute, George Mason University, Arlington, VA, August 11, 2014.

``Data Analysis for Humanists,'' workshop instructor at THATCamp American Historical Association, 
Washington, DC, January 5, 2014.

``Data Analysis for Humanists,'' workshop instructor THATCamp American Academy of Religion, Baltimore, November 22, 2013.

Invited participant, Speaking in Code symposium, University of Virginia, 
Charlottesville, VA, November 4--5, 2013.

Erin Bartram and Lincoln A. Mullen, ``How to Use a Database for Historical 
Research,'' THATCamp New England, University of Connecticut at Storrs, October 
18, 2013.

``Returning to the Fold: Nineteenth-Century Converts Who Returned to
Their Original Faith,'' talk given at Kronstadt Moment/Road to Damascus,
New School for Social Research, New York, April 26--27, 2013.

``The American Converts Database and the Monographic Dissertation,''
talk for the panel ``Digital Methods and the Traditional Dissertation,''
given at Digital Humanities: The Next Generation, Simmons College,
Boston, March 15, 2013.

``Catholic Converts in the Nineteenth-Century Market of Souls,'' paper
presented at the annual meeting of the American Catholic Historical
Association, New Orleans, January 4, 2013.

``The Humanist's Operating System; or, Scholarship in Plain Text,'' THATCamp 
New England 2012, Brown University, October 20, 2012.

``Does the Soul Have a History?'' paper presented at the biennial
meeting of the Conference on Faith and History, Gordon College, October
5, 2012.

``Six Days Shalt Thou Labor': Work, Sabbath Observance, and Cultural
Conversion in John Eliot's Mission to the Indians,'' paper presented at
the annual meeting of the American Society for Church History, Chicago,
January 7, 2012.

``The Vocabulary of Conversion: Text Mining the East Windsor Conversion
Relations,'' paper presented at the annual meeting of the American
Society for Church History, Boston, January 9, 2011.

% ``\,`Call to Remembrance the Former Days': The Use of History in New
% England Occasional Sermons, 1660--1684,'' paper presented at the
% Christianity and American History conference, Liberty University, April
% 2007.

% ``The Interrelationship of Reason, Faith, and Revelation in St.~Thomas
% Aquinas,'' paper presented at the annual meeting of the South Carolina
% Historical Association, March 2006.

% \subsection{encyclopedia articles}\label{encyclopedia-articles}
% 
% Contributions to \emph{The Encyclopedia of American Reform Movements},
% \emph{The Encyclopedia of the Early Republic and Antebellum America},
% \emph{The Encyclopedia of American Immigration},
% \emph{The Encyclopedia of U.S. Political History},
% \emph{The Encyclopedia of the Veteran in America},
% \emph{The Political Lincoln: An Encyclopedia}.

\subsection{external grants \& fellowships}\label{grants-and-fellowships}

``America's Public Bible: Machine-Learning Detection of Biblical Quotations across Library of Congress Collections via Cloud Computing,'' Computing Cultural Heritage in the Cloud, Library of Congress Labs (2021--2022): \$77,500.

Lincoln A. Mullen, John G. Turner, Jessica Mack, and Zev Eleff, "Collecting Together: A Portal and Coordinated Collecting Effort for the American Jewish Community During COVID-19," Lippman Kanfer Foundation for Living Torah, Jim Joseph Foundation, Charles and Lynn Schusterman Family Foundation, and The Russell Berrie Foundation (2021--2023): \$107,000.

Lincoln A. Mullen, ``Micro-Donations for Galleries, Libraries, Archives, and
Museums via Web Monetization and the Omeka S Platform,'' Grant for the Web
(2020--2021): \$49,949.

National Research Fellow, The Center for the Study of Religion \& American
Culture, IUPUI (2020--).

Jessica Otis and Lincoln A. Mullen, ``DataScribe: Enabling Structured Data Transcription in the Omeka S Web
Platform,'' Digital Humanities Advancement Grant from the National Endowment for the Humanities (2019--2022): \$324,733.

Lincoln A. Mullen and John G. Turner, ``Mapping American Religious Ecologies,'' Humanities Collections and Reference Resources grant from the National Endowment for the Humanities (2019--2022): \$349,944.

Young Scholars in American Religion, Center for the Study of Religion and American Culture, IUPUI (2019--2021).

Lincoln A. Mullen, Stephen Robertson, and Sheila Brennan, ``Gerda Henkel Postdoctoral Fellow in Digital History,'' contract with German Historical Institute (2018--2021): \$28,991.

Stephen Robertson and Lincoln A. Mullen, ``Model Articles for Argumentative Digital History,'' grant from the Andrew W. Mellon Foundation (2018--2021): \$125,000.

Lincoln A. Mullen and John G. Turner, ``Mapping American Religion,'' Faculty Research and Development Award from College of Humanities and Social Sciences, George Mason University (2018): \$7,998.

Stephen Robertson and Lincoln A. Mullen, ``Arguing with Digital History,'' grant from the Andrew W. Mellon Foundation (2017): \$29,500.

Sheila Brennan and Lincoln A. Mullen, ``Mapping Early American Elections,'' Humanities Collections and Reference Resources grant from the National Endowment for the Humanities (2016--2019): \$200,000. 

Mellon Dissertation Year Fellowship (2014--2015, declined).

Mellon Dissertation Research Award, Brandeis University (2012).

Award to attend ``Congregations and Social Change'' seminar, Calvin College 
(2011).

Kate B. and Hall J. Peterson Fellowship, American Antiquarian Society (2013). \$1,850.

Irving and Rose Crown Fellowship, Brandeis University (2009--2014).

\subsection{prizes \& awards}\label{prizes-and-awards}

Best First Book in the History of Religions for \emph{The Chance of Salvation}, American Academy of Religion (2018).

First prize in the Chronicling America Data Challenge for \emph{America's Public Bible}, National Endowment for the Humanities (2016).

University Prize Instructorship, Brandeis University (2013).

Ruth B. Fein Prize, American Jewish Historical Society (2012). 

\subsection{phd dissertations supervised}\label{dissertations}

Kristofer Stinson, ``Shadows and Solid Things: God, History, and Archeology in the Atlantic World'' (PhD dissertation, George Mason University, in progress).

Jannelle Legg, ``\,`With Eloquent Fingers He Preached': 
The Protestant Episcopal Mission to the Deaf'' (PhD dissertation, George Mason University, 2021).

\subsection{teaching}\label{teaching}

George Mason University:

\vspace{-0.15in}

\begin{itemize}
    \tightlist
  \item American Scriptures 
  \item Church and State in America
  \item Computational History 
  \item Digital History Practicum
  \item Global History of Christianity 
  \item Programming for Historians 
  \item Religion and Capitalism in the US 
  \item Text Analysis for Historians 
  \item The Digital Past: Reconstruction and Redemption
\end{itemize}

\vspace{-0.1in}

Brandeis University:

\vspace{-0.15in}

\begin{itemize}
    \tightlist
  \item
    Mapping Boston's Religions: A Digital History Seminar 
  \item
    Religious Pluralism and the American State (fall 2012)
\end{itemize}

\subsection{service to the profession}\label{service-profession}

Referee for these journals, publishers, grant agencies, and academic software 
repositories: \emph{American Historical Review}, Chapman and Hall, 
\emph{Debates in the Digital Humanities}, \emph{Digital Humanities Quarterly}, 
Duke University Press, Harvard University Press, \emph{IJHAC: A Journal of 
  Digital Humanities}, \emph{Journal of the American Academy of Religion}, 
\emph{Journal of Mormon History}, \emph{Journal of Social History}, \emph{Law 
  and History Review}, National Endowment for the Humanities, O'Reilly, 
rOpenSci, \emph{R Journal}, Stanford University Press, \emph{U.S. Catholic
Historian}.

Member, American History Task Force, \emph{Educating for American Democracy} (2020).

Editorial board, rOpenSci (2018--2020).

Conference organizer and editor with Stephen Robertson, \emph{Current Research 
  in Digital History} (2017--).

Project advisor for Edward Baptist et al, \emph{Freedom on the Move}, Cornell 
University, 2014--2017.

Co-organizer, THATCamp American Historical Association 2016, Georgia State University, January 6, 2016.

Web editor, \emph{Journal of Southern Religion} (2011--2015).

Co-organizer, THATCamp New England 2012, held at Brown University,
October 19--20, 2012.

Lead organizer, THATCamp New England 2011, held at Brandeis University,
October 21--22, 2011.

Co-organizer, THATCamp New England 2010, held at Wentworth Institute of
Technology, November 13--14, 2010.

% List editor, H-GRAD (2009--2011).

\subsection{service to the university}\label{service-university}

Faculty Grievance Committee, College of Humanities and Social Sciences, GMU (2020--).

Undergraduate Committee, History and Art History, GMU (2020--).

PhD Admissions Committee, History and Art History, GMU (2014--15, 2017--).

Job search committee, History and Art History, GMU (2018--2019).

Mason Core IT requirement assessment committee, CHSS, GMU (fall 2018).

Dean's Challenge Review committee, CHSS, GMU (spring 2018).

Communication and Alumni Relations Committee, History and Art History, GMU 
(2015--2017).

Teaching with Technology Committee, Brandeis University (2010--2012).

% Co-convener, Religion Working Group, Brandeis University (2012--2013).

% \subsection{languages \& digital humanities
%   skills}\label{languages-and-digital-humanities-skills}

% Reading knowledge of ancient (Koine) Greek.

% Data analysis: primarily R (programming language), D3.js (visualizations), QGIS
% (mapping).

\subsection{professional memberships}\label{professional-memberships}

\begin{itemize}
    \tightlist
    \item American Association of University Professors
    \item American Historical Association
    \item American Society of Church History
    \item Conference on Faith and History
\end{itemize}

\end{document}
