% Curriculum vitae

% Lincoln A. Mullen | lincoln@lincolnmullen.com | http://lincolnmullen.com

\documentclass[11pt]{article}
\usepackage{microtype}
\frenchspacing
\usepackage[letterpaper,margin=1in]{geometry} 
\setlength\parindent{0in}
\setlength\parskip{6pt}
\setlength{\emergencystretch}{3em}
% \def\ind{\hangindent=1 true cm\hangafter=1 \noindent}
\usepackage[osf,sc]{mathpazo}
\usepackage{inconsolata}
\usepackage{fancyhdr}
\pagestyle{plain}
\frenchspacing
% \usepackage{multicol}
% \usepackage{graphicx}
% \usepackage[usenames,dvipsnames]{color}

% % ---- MARGIN YEARS
% \usepackage{marginnote}
% \newcommand{\years}[1]{\marginnote{#1}[4pt]}
% \renewcommand{\raggedleftmarginnote}{}
% \setlength{\marginparsep}{2pt}
% \reversemarginpar

% HEADINGS
\usepackage{sectsty} 
\usepackage{titlesec}
\usepackage[normalem]{ulem} 
\sectionfont{\rmfamily\mdseries\Large} 
\subsectionfont{\rmfamily\mdseries\scshape\normalsize} 
\subsubsectionfont{\rmfamily\bfseries\upshape\normalsize} 
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsubsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
% disables chapter, section and subsection numbering
\setcounter{secnumdepth}{-1} 

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% PDF SETUP
\PassOptionsToPackage{hyphens}{url}\usepackage[hidelinks, breaklinks, pdftex, pdftitle={Lincoln A.  Mullen - CV}, pdfauthor={Lincoln A. Mullen}]{hyperref}  

% DOCUMENT
\begin{document}
\thispagestyle{fancy}
\fancyfoot{}
\fancyhead{}
\renewcommand{\headrulewidth}{0pt}
%%% The next line will put the date revised in footer of first page
\rfoot{\scriptsize Current as of \today}

\hfill\hfill\hfill
\hfill\hfill\hfill
\hfill\hfill\hfill
\hfill\hfill\hfill
\begin{minipage}[t]{1.4in}
  \flushleft{\scriptsize  \texttt{\href{mailto:lincoln@lincolnmullen.com}{lincoln@lincolnmullen.com}}} \\
  \vspace{-0.065in}{\scriptsize  \url{http://lincolnmullen.com}}
\end{minipage}
\hfill
\begin{minipage}[t]{1.9in}
  \flushleft{{\scriptsize {Department of History \& Art History} \\ George 
      Mason University \\ 4400 University Drive, MSN 3G1 \\ \vspace{-0.05in} 
      Fairfax, VA 22030}}
\end{minipage}

\vspace{0.1in}

{\Large Lincoln A. Mullen}\\[-0.1in]

\subsection{positions}\label{appointment}

Assistant professor, \href{http://historyarthistory.gmu.edu/}{Dept.
  of History \& Art History}, George Mason University (2014--present).

\subsection{education}\label{education}

PhD history, Brandeis University (2014). 

\hfill\begin{minipage}{6.25in}

  Dissertation: ``\href{/research/\#dissertation}{The Varieties of American 
    Conversion: The Origins of Religious Choice in the United States}.'' 

\end{minipage}

\vspace{0.05in}

MA history, Brandeis University (2011).

BA \& MA history, Bob Jones University (2006/2008).

\subsection{recent grants \& awards}

Stephen Robertson (co-PI) and Lincoln Mullen (co-PI), "Arguing with Digital 
History," grant from the Andrew W. Mellon Foundation, 2017. Amount: \$29,500.

First prize in the ``Chronicling America Data Challenge,'' National Endowment 
for the Humanities, for \emph{America's Public Bible}, awarded July 2016. 
Amount: \$5,000.

Sheila Brennan (co-PI), Lincoln Mullen (co-PI), Rosemarie Zagarri (lead 
historian), \emph{Mapping Early American Elections}, Humanities Collections 
and Reference Resources grant, National Endowment for the Humanities, 
2016--2019. Amount: \$200,000. 

\subsection{book and monograph}

\emph{America's Public Bible: Biblical Quotations in U.S. Newspapers},
digital monograph, (Stanford University Press, under contract and forthcoming 
2018): \url{http://americaspublicbible.org}.

\emph{The Chance of Salvation: A History of Conversion in America} (Harvard 
University Press, 2017).

\subsection{select recent publications and projects}

Kellen Funk and Lincoln A. Mullen, ``The Spine of American Law: Digital Text 
Analysis and U.S. Legal Practice,'' \emph{American Historical Review} 123, no. 1 (accepted for publication February 2018). 

``A Braided Narrative for Digital History,'' in \emph{Debates in the Digital 
  Humanities 2018}, ed. Matthew K. Gold and Lauren F. Klein (University of 
Minnesota Press, forthcoming 2018).

Lincoln Mullen, Margaret Bendroth, Thomas Kidd, Keith Harper, and Robert W. 
Prichard, ``The Uses of Denominational History,'' \emph{Fides et Historia} 49, 
no. 2 (forthcoming fall 2017).

Kellen Funk and Lincoln Mullen, ``A Servile Copy: Text Reuse and Medium Data 
in American Civil Procedure,'' in \emph{Forum: Die geisteswissenschaftliche 
  Perspektive: Welche Forschungsergebnisse lassen Digital Humanities 
  erwarten?} [\emph{Forum: With the Eyes of a Humanities Scholar: What Results 
  Can We Expect from Digital Humanities?}], 24 \emph{Rechtsgeschichte} 
[\emph{Legal History}] (2016): 341--43. DOI: 
\href{http://dx.doi.org/10.12946/rg24/341-343}{10.12946/rg24/341-343}

Cameron Blevins and Lincoln Mullen, ``Jane, John \ldots{} Leslie? A
Historical Method for Algorithmic Gender Prediction,'' \emph{Digital
  Humanities Quarterly} 9, no. 3 (2015): 
\url{http://www.digitalhumanities.org/dhq/vol/9/3/000223/000223.html}

``Lynching, Visualization, and Visibility,'' \emph{Journal of Southern 
  Religion} 17 (2015): \url{http://jsreligion.org/issues/vol17/mullen.html}

``The Contours of Conversion to Catholicism in the Nineteenth Century,''
\emph{U.S. Catholic Historian} 32, no. 2 (2014): 1--27. DOI:
\href{http://dx.doi.org/10.1353/cht.2014.0007}{10.1353/cht.2014.0007}

``Using Metadata and Maps to Teach the History of Religion,''
\emph{Transformations: The Journal of Inclusive Scholarship and
  Pedagogy}, 25, no. 1 (2014): 112--118.

``Digital Humanities Is a Spectrum; or, We're All Digital Humanists
Now,'' in Melissa Terras, Edward Vanhoutte, and Julianne Nyhan, eds.,
\emph{Defining Digital Humanities: A Reader} (Ashgate, 2013), 237--38.

``A Narrative of the Troubles in the Second Church in Windsor,
1735--1741,'' by Roger Wolcott, \emph{Journal of Jonathan Edwards
  Studies} 2, no. 2 (2012): 83--142.

\subsection{select recent talks and conference presentations}

Kellen Funk and Lincoln Mullen, ``Text Reuse for Digital Legal History,'' 
invited talk and workshop, American Society for Legal History, Toronto, October 27, 2016.

Panel chair and organizer, ``The Uses of Denominational History,'' Conference 
on Faith and History, Virginia Beach, Virginia, October 21, 2016.

``The Bible in the Newspaper,'' invited talk at the NEH National Digital 
Newspaper Program annual meeting, Washington, DC, September 14, 2016.

``Mapping Denominational Statistics in the Nineteenth Century,'' discussant 
for ``Digital Humanities Roundtable: Mapping the Early Republic,'' annual 
meeting of the Society for Historians of the Early American Republic, New 
Haven, July 21--24, 2016.

``Choosing the New Birth: The Protestant Development of the Sinner's Prayer in 
Early America,'' invited paper at the Virginia Colloquium in American 
Religion, University of Virginia, April 1, 2016.

``The Religion of Children and Families in the Nineteenth-century United 
States,'' paper presented at the annual meeting of the American Society of 
Church History, Atlanta, January 10, 2016.

``Converts and the Category of Irreligion in the Nineteenth-century
United States,'' paper presented at the annual meeting of the
Organization of American Historians, St.~Louis, April 16--19, 2015.

``Mapping Boston's Religions: Next Steps in Mapping U.S. Religious History,'' 
for the panel ``Mapping Religious Space: Four American Cities from the 
Colonial Era to the Twentieth Century'' at the annual meeting of the American 
Society of Church History, New York, January 2--5, 2015.  
\url{http://lincolnmullen.com/projects/asch-2015/}

\end{document}

