% Curriculum vitae

% Lincoln A. Mullen | lincoln@lincolnmullen.com | http://lincolnmullen.com

\documentclass[11pt]{article}
\usepackage{microtype}
\frenchspacing
\usepackage[letterpaper,margin=1in]{geometry} 
\setlength\parindent{0in}
\setlength\parskip{6pt}
\setlength{\emergencystretch}{3em}
% \def\ind{\hangindent=1 true cm\hangafter=1 \noindent}
\usepackage[osf,sc]{mathpazo}
\usepackage{inconsolata}
\usepackage{fancyhdr}
\pagestyle{plain}
\frenchspacing
% \usepackage{multicol}
% \usepackage{graphicx}
% \usepackage[usenames,dvipsnames]{color}

% % ---- MARGIN YEARS
% \usepackage{marginnote}
% \newcommand{\years}[1]{\marginnote{#1}[4pt]}
% \renewcommand{\raggedleftmarginnote}{}
% \setlength{\marginparsep}{2pt}
% \reversemarginpar

% HEADINGS
\usepackage{sectsty} 
\usepackage{titlesec}
\usepackage[normalem]{ulem} 
\sectionfont{\rmfamily\mdseries\Large} 
\subsectionfont{\rmfamily\mdseries\scshape\normalsize} 
\subsubsectionfont{\rmfamily\bfseries\upshape\normalsize} 
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsubsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
% disables chapter, section and subsection numbering
\setcounter{secnumdepth}{-1} 

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% PDF SETUP
\PassOptionsToPackage{hyphens}{url}\usepackage[hidelinks, breaklinks, pdftex, pdftitle={Lincoln A.  Mullen - CV}, pdfauthor={Lincoln A. Mullen}]{hyperref}  

% DOCUMENT
\begin{document}
\thispagestyle{fancy}
\fancyfoot{}
\fancyhead{}
\renewcommand{\headrulewidth}{0pt}
%%% The next line will put the date revised in footer of first page

\hfill\hfill\hfill
\hfill\hfill\hfill
\hfill\hfill\hfill
\hfill\hfill\hfill
\begin{minipage}[t]{1.6in}
  \flushleft{\scriptsize  \texttt{\href{mailto:lincoln@lincolnmullen.com}{lincoln@lincolnmullen.com}}} \\
  \vspace{-0.065in}{\scriptsize  \url{https://lincolnmullen.com}} \\
  \vspace{-0.065in}{\scriptsize  ORCID: 
  \href{https://orcid.org/0000-0001-5103-6917}{\texttt{0000-0001-5103-6917}}}
\end{minipage}
\hfill
\begin{minipage}[t]{1.9in}
  \flushleft{{\scriptsize {Department of History \& Art History} \\ George 
      Mason University \\ 4400 University Drive, MSN 3G1 \\ \vspace{-0.05in} 
      Fairfax, VA 22030}}
\end{minipage}

\vspace{0.1in}

{\Large Lincoln A. Mullen}\\[-0.1in]

\subsection{appointments}\label{Appointments}


Associate professor, Dept. of History \& Art History, George Mason University (2019--).

Director of computational history, Roy Rosenzweig Center for History and New Media (2018--).

Assistant professor, Dept. of History \& Art History, George Mason University (2014--2019).

\subsection{education}\label{education}

PhD history, Brandeis University (2014). 

\subsection{selected publications and \& projects}\label{books}

\emph{America's Public Bible: Biblical Quotations in U.S. Newspapers} (Stanford University Press, under contract): \url{http://americaspublicbible.org}.

\emph{American Religious Ecologies}, Roy Rosenzweig Center for History and New Media, George Mason University (in progress, 2018--): \url{http://religiousecologies.org}. (principal investigator)

Ben Marwick, Carl Boettiger, and Lincoln A. Mullen, ``Packaging Data Analytical Work Reproducibly using R (and Friends)'' \emph{American Statistician} 72, no. 1 (2018): 80--88, \url{https://doi.org/10.1080/00031305.2017.1375986}.

Kellen Funk and Lincoln A. Mullen, ``The Spine of American Law: Digital Text Analysis and U.S. Legal Practice,'' \emph{American Historical Review} 123, no.  1 (2018): 132--164, \url{https://doi.org/10.1093/ahr/123.1.132}.

\emph{The Chance of Salvation: A History of Conversion in America} (Harvard University Press, 2017).

\emph{Mapping Early American Elections}, Roy Rosenzweig Center for History and New Media, George Mason University (2016--2019): \url{http://earlyamericanelections.org}. (principal investigator)

\subsection{selected grants \& prizes}\label{grants-and-fellowships}

Jessica Otis and Lincoln A. Mullen, ``DataScribe: Enabling Structured Data Transcription in the Omeka S Web
Platform,'' National Endowment for the Humanities (2019--2022): \$324,733.

Lincoln A. Mullen and John G. Turner, ``Mapping American Religious Ecologies,'' Humanities Collections and Reference Resources grant from the National Endowment for the Humanities (2019--2022): \$349,944.

Best First Book in the History of Religions for \emph{The Chance of Salvation}, American Academy of Religion (2018).

First prize in the Chronicling America Data Challenge for \emph{America's Public Bible}, National Endowment for the Humanities (2016).

\end{document}

