% Curriculum vitae

% Lincoln A. Mullen | lincoln@lincolnmullen.com | http://lincolnmullen.com

\documentclass[10pt]{article}
\usepackage{microtype}
\frenchspacing
\usepackage[letterpaper,margin=1in]{geometry} 
\setlength\parindent{0in}
\setlength\parskip{6pt}
\setlength{\emergencystretch}{3em}
% \def\ind{\hangindent=1 true cm\hangafter=1 \noindent}
\usepackage[osf,sc]{mathpazo}
\usepackage{inconsolata}
\usepackage{fancyhdr}
\pagestyle{plain}
\frenchspacing
% \usepackage{multicol}
% \usepackage{graphicx}
% \usepackage[usenames,dvipsnames]{color}

% % ---- MARGIN YEARS
% \usepackage{marginnote}
% \newcommand{\years}[1]{\marginnote{#1}[4pt]}
% \renewcommand{\raggedleftmarginnote}{}
% \setlength{\marginparsep}{2pt}
% \reversemarginpar

% HEADINGS
\usepackage{sectsty} 
\usepackage{titlesec}
\usepackage[normalem]{ulem} 
\sectionfont{\rmfamily\mdseries\Large} 
\subsectionfont{\rmfamily\mdseries\scshape\normalsize} 
\subsubsectionfont{\rmfamily\bfseries\upshape\normalsize} 
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsubsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
% disables chapter, section and subsection numbering
\setcounter{secnumdepth}{-1} 

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% PDF SETUP
\PassOptionsToPackage{hyphens}{url}\usepackage[hidelinks, breaklinks, pdftex, pdftitle={Lincoln A.  Mullen - CV}, pdfauthor={Lincoln A. Mullen}]{hyperref}  

% DOCUMENT
\begin{document}
\thispagestyle{fancy}
\fancyfoot{}
\fancyhead{}
\renewcommand{\headrulewidth}{0pt}
%%% The next line will put the date revised in footer of first page
\rfoot{\scriptsize Current as of \today}

\hfill\hfill\hfill
\hfill\hfill\hfill
\hfill\hfill\hfill
\hfill\hfill\hfill
\begin{minipage}[t]{1.4in}
  \flushleft{\scriptsize  \texttt{\href{mailto:lincoln@lincolnmullen.com}{lincoln@lincolnmullen.com}}} \\
  \vspace{-0.065in}{\scriptsize  \url{http://lincolnmullen.com}}
\end{minipage}
\hfill
\begin{minipage}[t]{1.9in}
  \flushleft{{\scriptsize {Department of History \& Art History} \\ George 
      Mason University \\ 4400 University Drive, MSN 3G1 \\ \vspace{-0.05in} 
      Fairfax, VA 22030}}
\end{minipage}

\vspace{0.1in}

{\Large Lincoln A. Mullen}\\[-0.1in]

\subsection{appointment}\label{appointment}

Assistant professor, \href{http://historyarthistory.gmu.edu/}{Department of 
  History and Art History}, George Mason University (2014--present)

\subsection{education}\label{education}

PhD history, Brandeis University (2014)

\subsection{selected publications}

\emph{The Chance of Salvation: A History of Conversion in America} (Harvard 
University Press, under contract)

``A Braided Narrative for Digital History,'' in \emph{Debates in the Digital 
  Humanities 2017}, ed. Matthew K. Gold and Lauren F. Klein (University of 
Minnesota Press, forthcoming 2017).

Kellen Funk and Lincoln Mullen, ``A Servile Copy: Text Reuse and Medium Data 
in American Civil Procedure,'' in \emph{Forum: Die geisteswissenschaftliche 
  Perspektive: Welche Forschungsergebnisse lassen Digital Humanities 
  erwarten?} [\emph{Forum: With the Eyes of a Humanities Scholar: What Results 
  Can We Expect from Digital Humanities?}], 24 \emph{Rechtsgeschichte} 
[\emph{Legal History}] (forthcoming, 2016).

Cameron Blevins and Lincoln Mullen, ``Jane, John \ldots{} Leslie? A
Historical Method for Algorithmic Gender Prediction,'' \emph{Digital
  Humanities Quarterly} 9, no. 3 (2015): 
\url{http://www.digitalhumanities.org/dhq/vol/9/3/000223/000223.html}.

``Lynching, Visualization, and Visibility,'' \emph{Journal of Southern 
  Religion} 17 (2015): \url{http://jsreligion.org/issues/vol17/mullen.html}.

``The Contours of Conversion to Catholicism in the Nineteenth Century,''
\emph{U.S. Catholic Historian} 32, no. 2 (2014): 1--27. DOI:
\href{http://dx.doi.org/10.1353/cht.2014.0007}{10.1353/cht.2014.0007}

``Using Metadata and Maps to Teach the History of Religion,''
\emph{Transformations: The Journal of Inclusive Scholarship and
  Pedagogy}, 24, no. 3 (2014): 34--40.

``Digital Humanities Is a Spectrum; or, We're All Digital Humanists
Now,'' in Melissa Terras, Edward Vanhoutte, and Julianne Nyhan, eds.,
\emph{Defining Digital Humanities: A Reader} (Ashgate, 2013).

``A Narrative of the Troubles in the Second Church in Windsor,
1735--1741,'' by Roger Wolcott, \emph{Journal of Jonathan Edwards
  Studies} 2, no. 2 (2012): 83--142.

\subsection{selected digital projects}\label{digital-projects}

\emph{America's Public Bible: Biblical Quotations in U.S. Newspapers}, 
website, code, and datasets (2016--): \url{http://americaspublicbible.org}

Sheila Brennan, Lincoln Mullen, Rosemarie Zagarri, et al., 
\emph{Mapping Early American Elections} (2016--)

``Divergence in U.S. Sex Ratios by County, 1820--2010.'' \url{http://lincolnmullen.com/projects/sex-ratios/}

``The Spread of U.S.  Slavery, 1790--1860. 
\url{http://lincolnmullen.com/projects/slavery/}

``Paulists Missions, 1851--1906.'' \url{http://lincolnmullen.com/projects/paulists-map/}

\end{document}

