% Curriculum vitae

% Lincoln A. Mullen | lincoln@lincolnmullen.com | https://lincolnmullen.com

\documentclass[11pt]{article}
\usepackage{microtype}
\frenchspacing
\usepackage[letterpaper,margin=1in]{geometry} 
\setlength\parindent{0in}
\setlength\parskip{6pt}
\setlength{\emergencystretch}{3em}
% \def\ind{\hangindent=1 true cm\hangafter=1 \noindent}

\usepackage[]{plex-serif}
\usepackage[mb]{plex-sans}
\usepackage[scale=0.95]{plex-mono}

\usepackage{fancyhdr}
\pagestyle{plain}
% \usepackage{multicol}
% \usepackage{graphicx}
% \usepackage[usenames,dvipsnames]{color}

% % ---- MARGIN YEARS
% \usepackage{marginnote}
% \newcommand{\years}[1]{\marginnote{#1}[4pt]}
% \renewcommand{\raggedleftmarginnote}{}
% \setlength{\marginparsep}{2pt}
% \reversemarginpar

% HEADINGS
\usepackage{sectsty} 
\usepackage{titlesec}
\usepackage[normalem]{ulem} 
\sectionfont{\sffamily\bfseries\Large} 
\subsectionfont{\sffamily\bfseries\scshape\normalsize} 
\subsubsectionfont{\sffamily\bfseries\upshape\normalsize} 
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsubsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
% disables chapter, section and subsection numbering
\setcounter{secnumdepth}{-1} 

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% PDF SETUP
\PassOptionsToPackage{hyphens}{url}\usepackage[hidelinks, breaklinks, pdftex, pdftitle={Lincoln A.  Mullen - CV}, pdfauthor={Lincoln A. Mullen}]{hyperref}  

% DOCUMENT
\begin{document}
\thispagestyle{fancy}
\fancyfoot{}
\fancyhead{}
\renewcommand{\headrulewidth}{0pt}
%%% The next line will put the date revised in footer of first page
\rfoot{\scriptsize Current as of \today}

\hfill\hfill\hfill
\hfill\hfill\hfill
\hfill\hfill\hfill
\hfill\hfill\hfill
\begin{minipage}[t]{2.2in}
  \flushleft{\scriptsize  \texttt{\href{mailto:lincoln@lincolnmullen.com}{lincoln@lincolnmullen.com}}} \\
  \vspace{-0.065in}{\scriptsize  \url{https://lincolnmullen.com}} \\
  \vspace{-0.065in}{\scriptsize  ORCID: 
  \href{https://orcid.org/0000-0001-5103-6917}{\texttt{0000-0001-5103-6917}}}
\end{minipage}
\hfill
\begin{minipage}[t]{3.0in}
  \flushleft{{\scriptsize {Roy Rosenzweig Center for History and New Media \\ Department of History and Art History \\ \vspace{-0.065in} George Mason University, Fairfax, Virginia}}}
\end{minipage}

\vspace{0.4in}

{\Large\sffamily\bfseries Lincoln A. Mullen}\\[-0.1in]


\subsection{Current appointments}\label{Appointments}

Executive director, Roy Rosenzweig Center for History and New Media.

Professor, Department of History \& Art History, George Mason University.

\subsection{Education}\label{education}

PhD in history, Brandeis University (2014). 

\subsection{Books \& selected digital projects}\label{books}

John Turner, Lincoln Mullen, et al., \emph{Antisemitism, U.S.A.: A History Podcast} (2024): \url{https://www.r2studios.org/show/Antisemitism-USA/}.

\emph{America's Public Bible: Biblical Quotations in U.S. Newspapers} (Stanford University Press, 2023): \url{https://americaspublicbible.org}.

\emph{American Religious Ecologies}, Roy Rosenzweig Center for History and New Media (in progress, 2018--): \url{https://religiousecologies.org}. (project director with John Turner)

% \emph{Models of Argument-Driven Digital History}, Roy Rosenzweig Center for History and New Media, George Mason University (2021): \url{https://model-articles.rrchnm.org}. Special section, "Arguing with Digital Histories, edited by Stephen Robertson and Lincoln Mullen, \emph{Journal of Social History} 54, no. 4 (2021): \url{https://academic.oup.com/jsh/issue/54/4}. 

\emph{Collecting These Times: American Jewish Experiences of the Pandemic}, Roy Rosenzweig Center for History and New Media, George Mason University (2021--2022): \url{https://collectingthesetimes.org}. (co-project director)

\emph{Mapping Early American Elections}, Roy Rosenzweig Center for History and New Media (2016--2019): \url{https://earlyamericanelections.org}. (project director)

\emph{The Chance of Salvation: A History of Conversion in America} (Harvard University Press, 2017).

\subsection{Selected peer-reviewed journal articles \& book chapters}\label{peer-reviewed}

Stephen Robertson and Lincoln A. Mullen, ``Arguing with Digital History: Patterns of Historical Interpretation,'' \emph{Journal of Social History} 54, no. 4 (2021): 1005--1022, \url{https://doi.org/10.1093/jsh/shab015}.

``The Making of America's Public Bible: Computational Text Analysis in Religious History,'' in \emph{Digital Humanities and Research Methods in Religious Studies: An Introduction}, edited by Christopher D. Cantwell and Kristian Petersen (DeGruyter, 2021), 31--52, \url{https://doi.org/10.1515/9783110573022-003}.

Ben Marwick, Carl Boettiger, and Lincoln A. Mullen, ``Packaging Data Analytical Work Reproducibly using R (and Friends)'' \emph{American Statistician} 72, no. 1 (2018): 80--88, \url{https://doi.org/10.1080/00031305.2017.1375986}.

Kellen Funk and Lincoln A. Mullen, ``The Spine of American Law: Digital Text Analysis and U.S. Legal Practice,'' \emph{American Historical Review} 123, no.  1 (2018): 132--164, \url{https://doi.org/10.1093/ahr/123.1.132}.

Cameron Blevins and Lincoln A. Mullen, ``Jane, John \ldots{} Leslie? A Historical Method for Algorithmic Gender Prediction,'' \emph{Digital Humanities Quarterly} 9, no. 3 (2015): \url{http://www.digitalhumanities.org/dhq/vol/9/3/000223/000223.html}. 

% ``The Contours of Conversion to Catholicism in the Nineteenth Century,'' \emph{U.S. Catholic Historian} 32, no. 2 (2014): 1--27, \url{https://doi.org/10.1353/cht.2014.0007}. 

\subsection{Selected external grants \& fellowships}\label{grants-and-fellowships}

Lincoln A. Mullen and John G. Turner, ``Mapping American Religious Ecologies,'' Humanities Collections and Reference Resources grant from the National Endowment for the Humanities (2023--2026): \$350,000.

John G. Turner, Lincoln A. Mullen, and Jeanette Patrick, ``The History of American Antisemitism: A Podcast,'' Henry Luce Foundation (2022--): \$50,000.

Lincoln A. Mullen and John Turner, ``The Denig Bible Project,'' Winterthur Museum, Garden, and Library (2022--): \$80,500.

Mills Kelly, Jessica Otis, and Lincoln A. Mullen, ``Building Financial Resilience in the Digital Humanities,'' Andrew W. Mellon Foundation (2021--2025): \$1,000,000.

Lincoln A. Mullen, ``America's Public Bible: Machine-Learning Detection of Biblical Quotations across Library of Congress Collections via Cloud Computing,'' Computing Cultural Heritage in the Cloud, Library of Congress Labs (2021--2022): \$77,500.

Lincoln A. Mullen, John G. Turner, Jessica Mack, and Zev Eleff, "Collecting Together: A Portal and Coordinated Collecting Effort for the American Jewish Community During COVID-19," Lippman Kanfer Foundation for Living Torah, Jim Joseph Foundation, Charles and Lynn Schusterman Family Foundation, and The Russell Berrie Foundation (2021--2023): \$107,000.

% Jessica Otis and Lincoln A. Mullen, ``DataScribe: Enabling Structured Data Transcription in the Omeka S Web Platform,'' Digital Humanities Advancement Grant from the National Endowment for the Humanities (2019--2022): \$324,733.

Lincoln A. Mullen and John G. Turner, ``Mapping American Religious Ecologies,'' Humanities Collections and Reference Resources grant from the National Endowment for the Humanities (2019--2022): \$349,944.

Stephen Robertson and Lincoln A. Mullen, ``Model Articles for Argumentative Digital History,'' grant from the Andrew W. Mellon Foundation (2018--2021): \$125,000.

Stephen Robertson and Lincoln A. Mullen, ``Arguing with Digital History,'' grant from the Andrew W. Mellon Foundation (2017): \$29,500.

Sheila Brennan and Lincoln A. Mullen, ``Mapping Early American Elections,'' Humanities Collections and Reference Resources grant from the National Endowment for the Humanities (2016--2019): \$200,000. 

Kate B. and Hall J. Peterson Fellowship, American Antiquarian Society (2013). 

\subsection{Selected prizes \& honors}\label{prizes-and-honors}

Presidential award for research excellence, George Mason University (2024).

% Young Scholars in American Religion, Center for the Study of Religion and American Culture, IUPUI (2019--2020).

Best First Book in the History of Religions for \emph{The Chance of Salvation}, American Academy of Religion (2018).

First prize in the Chronicling America Data Challenge for \emph{America's Public Bible}, National Endowment for the Humanities (2016).

% Ruth B. Fein Prize, American Jewish Historical Society (2012). 

% \subsection{selected courses}\label{teaching}

% \begin{itemize}
%   \tightlist
%   \item Religion and Capitalism in the US 
%   \item Global History of Christianity 
%   \item American Scriptures 
%   \item Computational History: Data Analysis and Visualization 
%   \item The Digital Past: Reconstruction and Redemption 
% \end{itemize}

\end{document}

