% Curriculum vitae

% Lincoln A. Mullen | lincoln@lincolnmullen.com | http://lincolnmullen.com

\documentclass[11pt]{article}
\usepackage{microtype}
\frenchspacing
\usepackage[letterpaper,margin=1in]{geometry} 
\setlength\parindent{0in}
\setlength\parskip{6pt}
\setlength{\emergencystretch}{3em}
% \def\ind{\hangindent=1 true cm\hangafter=1 \noindent}
\usepackage[osf,sc]{mathpazo}
\usepackage{inconsolata}
\usepackage{fancyhdr}
\pagestyle{plain}
\frenchspacing
% \usepackage{multicol}
% \usepackage{graphicx}
% \usepackage[usenames,dvipsnames]{color}

% % ---- MARGIN YEARS
% \usepackage{marginnote}
% \newcommand{\years}[1]{\marginnote{#1}[4pt]}
% \renewcommand{\raggedleftmarginnote}{}
% \setlength{\marginparsep}{2pt}
% \reversemarginpar

% HEADINGS
\usepackage{sectsty} 
\usepackage{titlesec}
\usepackage[normalem]{ulem} 
\sectionfont{\rmfamily\mdseries\Large} 
\subsectionfont{\rmfamily\mdseries\scshape\normalsize} 
\subsubsectionfont{\rmfamily\bfseries\upshape\normalsize} 
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
\titlespacing\subsubsection{0pt}{12pt plus 4pt minus 2pt}{0pt plus 2pt minus 2pt}
% disables chapter, section and subsection numbering
\setcounter{secnumdepth}{-1} 

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

% PDF SETUP
\PassOptionsToPackage{hyphens}{url}\usepackage[hidelinks, breaklinks, pdftex, pdftitle={Lincoln A.  Mullen - CV}, pdfauthor={Lincoln A. Mullen}]{hyperref}  

% DOCUMENT
\begin{document}
\thispagestyle{fancy}
\fancyfoot{}
\fancyhead{}
\renewcommand{\headrulewidth}{0pt}
%%% The next line will put the date revised in footer of first page
\rfoot{\scriptsize Current as of \today}

\hfill\hfill\hfill
\hfill\hfill\hfill
\hfill\hfill\hfill
\hfill\hfill\hfill
\begin{minipage}[t]{1.6in}
  \flushleft{\scriptsize  \texttt{\href{mailto:lincoln@lincolnmullen.com}{lincoln@lincolnmullen.com}}} \\
  \vspace{-0.065in}{\scriptsize  \url{https://lincolnmullen.com}} \\
  \vspace{-0.065in}{\scriptsize  ORCID: 
  \href{https://orcid.org/0000-0001-5103-6917}{\texttt{0000-0001-5103-6917}}}
\end{minipage}
\hfill
\begin{minipage}[t]{1.9in}
  \flushleft{{\scriptsize {Department of History \& Art History} \\ George 
      Mason University \\ 4400 University Drive, MSN 3G1 \\ \vspace{-0.05in} 
      Fairfax, VA 22030}}
\end{minipage}

\vspace{0.1in}

{\Large Lincoln A. Mullen}\\[-0.1in]

\subsection{appointment}\label{appointment}

Assistant professor, \href{http://historyarthistory.gmu.edu/}{Dept.
  of History \& Art History}, George Mason University (2014--present).

% Assistant director, Roy Rosenzweig Center for History and New Media, George 
% Mason University (2018--present).

\subsection{education}\label{education}

PhD history, Brandeis University (2014). 

MA history, Brandeis University (2011).

BA \& MA history, Bob Jones University (2006/2008).

\subsection{book \& digital projects}\label{books}

\emph{America's Public Bible: Biblical Quotations in U.S. Newspapers} 
(Stanford University Press, under contract). 
\url{http://americaspublicbible.org}.

Mapping Early American Elections project team, \emph{Mapping Early American Elections}, Roy Rosenzweig Center 
for History and New Media, George Mason University (2016--2019): 
\url{http://earlyamericanelections.org}.

\emph{The Chance of Salvation: A History of Conversion in America} (Harvard 
University Press, 2017). 
\url{http://www.hup.harvard.edu/catalog.php?isbn=9780674975620}.

\subsection{peer-reviewed journal articles \& book chapters}\label{peer-reviewed}

``A Braided Narrative for Digital History,'' in \emph{Debates in the Digital Humanities 2019}, ed. Matthew K. Gold and Lauren F. Klein (University of Minnesota Press, forthcoming 2019).

Ben Marwick, Carl Boettiger, and Lincoln A. Mullen, ``Packaging Data 
Analytical Work Reproducibly using R (and Friends)'' \emph{American 
Statistician} 72, no. 1 (2018): 80--88, \url{https://doi.org/10.1080/00031305.2017.1375986}.

Kellen Funk and Lincoln A. Mullen, ``The Spine of American Law: Digital Text Analysis and U.S. Legal Practice,'' \emph{American Historical Review} 123, no.  1 (2018): 132--164, \url{https://doi.org/10.1093/ahr/123.1.132}.

``Bibles and Tracts in Print Culture in America,'' \emph{Oxford Research Encyclopedia of Religion} (Oxford University Press, 2017). \url{ https://doi.org/10.1093/acrefore/9780199340378.013.412}.

Cameron Blevins and Lincoln A. Mullen, ``Jane, John \ldots{} Leslie? A Historical Method for Algorithmic Gender Prediction,'' \emph{Digital Humanities Quarterly} 9, no. 3 (2015): \url{http://www.digitalhumanities.org/dhq/vol/9/3/000223/000223.html}.

``The Contours of Conversion to Catholicism in the Nineteenth Century,'' \emph{U.S. Catholic Historian} 32, no. 2 (2014): 1--27, \url{https://doi.org/10.1353/cht.2014.0007}.

``Using Metadata and Maps to Teach the History of Religion,'' \emph{Transformations: The Journal of Inclusive Scholarship and Pedagogy}, 25, no. 1 (2014): 112--118, \url{https://doi.org/10.1353/tnf.2014.0008}.

\subsection{other academic publications}\label{other-academic}

``The Making of America's Public Bible: Computational Text Analysis in 
Religious History,'' in \emph{Introduction to Digital Humanities: Research 
Methods for the Study of Religion}, edited by Christopher D. Cantwell and 
Kristian Petersen (DeGruyter, forthcoming).

Lincoln A. Mullen, Margaret Bendroth, Thomas Kidd, Keith Harper, and Robert W. 
Prichard, ``The Uses of Denominational History,'' \emph{Fides et Historia} 49, 
no. 2 (2017): 57--66.

Arguing with Digital History working group, ``Digital History and Argument,'' 
white paper, Roy Rosenzweig Center for History and New Media (November 13, 
2017): \url{https://rrchnm.org/argument-white-paper/}. (primary author with 
     Stephen Robertson)

Kellen Funk and Lincoln A. Mullen, ``A Servile Copy: Text Reuse and Medium Data 
in American Civil Procedure,'' in \emph{Forum: Die geisteswissenschaftliche 
  Perspektive: Welche Forschungsergebnisse lassen Digital Humanities 
  erwarten?} [\emph{Forum: With the Eyes of a Humanities Scholar: What Results 
  Can We Expect from Digital Humanities?}], 24 \emph{Rechtsgeschichte} 
[\emph{Legal History}] (2016): 341--43, 
\url{https://doi.org/10.12946/rg24/341-343}.

``Lynching, Visualization, and Visibility,'' \emph{Journal of Southern 
  Religion} 17 (2015): \url{http://jsreligion.org/issues/vol17/mullen.html}

``A Narrative of the Troubles in the Second Church in Windsor,
1735--1741,'' by Roger Wolcott, \emph{Journal of Jonathan Edwards
  Studies} 2, no. 2 (2012): 83--142.

\subsection{peer-reviewed academic software}\label{academic-software}

Lincoln A. Mullen et al., ``Fast, Consistent Tokenization of Natural Language 
Text,'' \emph{Journal of Open Source Software}, 3, no. 23: 655 (2018), 
\url{https://doi.org/10.21105/joss.00655}.

Lincoln A. Mullen and Jordan F. Bratt, ``USAboundaries: Historical and 
Contemporary Boundaries of the United States of America,'' \emph{Journal of 
Open Source Software} 3, no. 23 (2018): 314, 
\url{https://doi.org/10.21105/joss.00314}.

``textreuse: Detect Text Reuse and Document Similarity,'' R package published 
by rOpenSci (2015--): 
\url{https://github.com/ropensci/textreuse}.

\subsection{selected grants, fellowships, \& prizes}\label{grants-and-fellowships}

Lincoln A. Mullen and John Turner, ``Mapping American Religion,'' Faculty 
Research and Development Award, CHSS, George Mason University (2018). \$7,998.

Stephen Robertson and Lincoln A. Mullen, ``Arguing with Digital History,'' grant 
from the Andrew W. Mellon Foundation (2017). \$29,500.

First prize in the Chronicling America Data Challenge, National Endowment 
for the Humanities, for \emph{America's Public Bible}, awarded July 2016. \$5,000.

Sheila Brennan and Lincoln A. Mullen, \emph{Mapping Early American Elections}, 
Humanities Collections and Reference Resources grant, National Endowment for 
the Humanities (2016--2019). \$200,000.

Kate B. and Hall J. Peterson Fellowship, American Antiquarian Society (2013). \$1,850.

Ruth B. Fein Prize, American Jewish Historical Society (2012). \$1,000.

\end{document}

